test

### 2020-07-16 manuscript/response_to_reviews.tex

Olson ME, Rosell JA, Martínez-Pérez C, León-Gómez C, Fajardo A, Isnard
S, Cervantes-Alcayde M-A, Echeverría A, Figueroa-Abúndiz, Segovia-Rivas
A, et al.~in press. Xylem vessel diameter-shoot length scaling:
ecological significance of porosity types and other traits. Ecological
Monographs.

Olson ME, Soriano D, Rosell JA, Anfodillo T, Donoghue MJ, Edwards EJ,
León-Gómez C, Dawson T, Camarero Martínez JJ, Castorena M, et al.~2018.
Plant height and hydraulic vulnerability to drought and cold.
Proceedings of the National Academy of Sciences 115: 7551--7556.

Rosell JA, Olson ME. 2014. Do lianas really have wide vessels? Vessel
diameter--stem length scaling in non-self-supporting plants.
Perspectives in Plant Ecology, Evolution and Systematics 16: 288--295.

@@

Sack L, Scoffoni C, McKown AD, Rawls M, Havran JC, Tran H, Tran T. 2012.
Developmentally based scaling of leaf venation architecture explains
global ecological patterns. Nature Communications 3: ncomms1835.

Selaya NG, Anten NPR. 2010. Leaves of pioneer and later-successional
trees have similar lifetime carbon gain in tropical secondary forest.
Ecology 91: 1102--1113. Sillett SC, Van Pelt R, Koch GW, Ambrose AR,
Carroll AL, Antoine ME, Mifsud BM. 2010. Increasing wood production
through old age in tall trees. Forest Ecology and Management 259:
976--994.

@@

Soriano D, Echeverría A, Anfodillo T, Rosell JA, Olson ME. in press.
Hydraulic traits vary as the result of tip-to-base conduit widening in
vascular plants. Journal of Experimental Botany.

Wheeler EA, Baas P, Rodgers S. 2007. Variations In Dicot Wood Anatomy: A
Global Analysis Based on the Insidewood Database. IAWA Journal 28:
229--258.

Williams CB, Anfodillo T, Crivellaro A, Lazzarin M, Dawson TE, Koch GW.
2019. Axial variation of xylem conduits in the Earth's tallest trees.
Trees 33: 1299--1311.

Zach A, Schuldt B, Brix S, Culmsee H, Culmsee H. 2010. Vessel diameter
and xylem hydraulic conductivity increase with tree height in tropical
rainforest trees in Sulawesi, Indonesia. Flora 205: 506--512.

\hypertarget{referee-3}{%
\subsection{Referee: 3}\label{referee-3}}

@@

Comments to the Author

McGregor and colleagues use a combination of long-term tree records and
functional trait data to explore the key drivers that shape the growth
resistance of different temperate tree species to extreme drought. They
find that that leaf hydraulic traits and tree size are strong predictors
of growth responses to drought -- with taller trees most affected.

I enjoyed the paper very much. It's clearly and succinctly written, and
brings together a range of complementary datasets to address some very
topical questions in forest ecology. I could definitely see the paper
being of interest to a broad readership. However, I do have some
important questions and suggestions about the analysis which I think
need more careful thought. Below I've listed my main concerns, following
which there are some other comments that the authors may want to take
into consideration in revising their paper.

@@

Main comments

L139-140: makes sense to not core live trees in the plot (surprised you
got permission to do this in 2011!). But doesn't this introduce a bias
in your analysis? Trees that died may have had very different responses
to drought that those which survived. Do you get similar results if you
analyse trees that lived and died separately?

\textbf{We agree that this could be a concern, but do not believe it is
applicable here, for two reasons. First, this would be more likely to
introduce a bias if the trees cored dead were killed by drought. We are
aware of studies showing differences in climate sensitivity of trees
killed by drought versus those that survived. However,these trees were
not killed by drought; there was no significant drought in the years in
which dead trees were cored or in the 3 previous years. Second, quoting
our previous publication using these cores (Helcoski et al.~2019): "
Chronologies of trees cored live and dead were pooled following analyses
showing similar climate sensitivity at least up to 2009 (that is
excluding 7--8 yr before death) for all four species with ≥ 10 cores in
each category (LITU, QURU, QUVE, FRAM; comparison plots available at
\url{https://github.c}
om/SCBI-ForestGEO/climate\_sensitivity\_cores/tree/master/
results/live\_vs\_dead).".}

\textbf{To clarify that this shouldn't be an issue, we have added the
following sentence (methods section): ``We note that drought was
probably not a cause of mortality for these trees, as monthly May-Aug
\(PDSI\) did not drop below -1.75 in these years or the three years
prior (2013-2017), and that trees cored dead displayed similar climate
sensitivity to trees cored live (Helcoski \emph{et al.}, 2019).''}

L165-167: I think this needs to be explained more clearly. Why are type
I errors unlikely and type II error possible? I also think there are
real issue with the analysis of crown position. Presumably on average
the crown illumination index of trees would have increased over the past
50 or so years (from suppressed to dominant) as trees grew and
neighbouring trees died. So I'm not convinced you can include this in
your models going back half a century. It's just not sensible to assume
that crown position would not have changed over such a long time period.

\textbf{We no longer attempt to use crown position to describe variation
in drought resistance. Instead, we now use it to characterize
\emph{contemporary} differences in microenvironmental conditions faced
by trees of different heights.}

L217-226: this is problematic because drought resistance (Rt) as defined
by Lloret et al.~(2011) assumes that tree growth (BAI in this case)
fluctuates around a long term mean that is stable through time. But this
is rarely/never the case with tree growth, which shows clear temporal
trends related to tree size/ontogeny. If you don't account for these
directional trends then your estimates of Rt will be biased. For
instance, if a tree is on a long-term trajectory of decreasing BAI over
time, when you calculate Rt you will overestimate the impact of the
drought (and vice versa for trees on an upward growth trajectory). So
you need to first detrend the tree ring series to remove long-term
growth trends (unless you can show that your trees exhibited no
long-term temporal trends in BAI). The fact that pre-drought conditions
were different for the three droughts is also a problem, but not much
you can do about this except acknowledge as you have done.

\href{https://github.com/SCBI-ForestGEO/McGregor_climate-sensitivity-variation/issues/92}{\emph{issue
\#92}}

\textbf{We do not agree that the \(Rt\) metric ``assumes that tree
growth (BAI in this case) fluctuates around a long term mean that is
stable through time.'' If this was true, \(Rt\) would be calculated by
dividing growth (BAI) in the drought year by the long-term mean growth
increment. Instead, \(Rt\) is calculated by dividing growth in the focal
year by the mean growth over a narrow window of preceding years (5 years
in this study). Even though there may be a long-term directional trend
in BAI, if you were to calculate the trend in BAI over each 5-year
increment, the trend could go in any direction. To account for such
trends, we tried an intervention time series analysis (ARIMA). Details
on the comparison between \(Rt\) and \(Rt_{ARIMA}\) are presented in the
responses to reviewer 4. In short, the ARIMA method yielded broadly
similar results, but tended to produce less reasonable estimates when
the difference between the two metrics was large, so we decided to
retain \(Rt\) as the focal metric. We now include the following content
on ARIMA in the manuscript:}

(\emph{insert text})

L260-261: This is rather strange. So for the same individual tree, size
was important in determining response to drought in one year but not in
the others? And that's for the years further back in time when the tree
would have been smallest? Couldn't that be interpreted as trees becoming
less susceptible to drought as they grow larger/older? It's also a
little concerning that results are very different across the three
droughts. Of these, the 1999 drought is the one I would tend to trust
most as stand structure and composition would have been most similar to
today.

@@

Other comments

L42-54: I think it would be worth making the link between growth
resilience and probability of mortality. Below are links to a couple of
papers that have recently shown that trees that are less resilient to
drought are also the ones most likely to die.
\url{https://nam02.safelinks.protection.outlook.com/?url=https\%3A\%2F\%2Fwww.nature.com\%2Farticles\%2Fs41467-020-14300-5.epdf\%3Fshared_access_token\%3DD9UngngFedreJeMMIQaYctRgN0jAjWel9jnR3ZoTv0PoKBL3IktPXOnnO0jnQ18EsS6uIPgICnN1RqVtsCGbwDx3K-1u5B0F1T9z3onm3gq-9mknjXKtuc0p7xxY3JipBCqwvtnrdqVNpsLdyzkNRw\%253D\%253D\&data=02\%7C01\%7CTeixeiraK\%40si.edu\%7Cda67e36e2ccc4277d4aa08d7ed356305\%7C989b5e2a14e44efe93b78cdd5fc5d11c\%7C0\%7C0\%7C637238685875974418\&sdata=6\%2B7kb11Bzq4LivdOhnR4frg1MEFGaX\%2FiIMUqJBG9gsM\%3D\&reserved=0}
\url{https://nam02.safelinks.protection.outlook.com/?url=https\%3A\%2F\%2Fwww.nature.com\%2Farticles\%2Fs41558-019-0583-9\&data=02\%7C01\%7CTeixeiraK\%40si.edu\%7Cda67e36e2ccc4277d4aa08d7ed356305\%7C989b5e2a14e44efe93b78cdd5fc5d11c\%7C0\%7C0\%7C637238685875974418\&sdata=DF9lSNfAFTjKmSWfb7FI8\%2FW4GDN4ljKxZK5NNS8eCxc\%3D\&reserved=0}

L80-101 \& L112-115: This is a nice summary of how traits can help us
understand species responses to drought. The only thing that is a little
strange is that you start by discussing commonly measured traits that
have been used to explore susceptibility to drought (e.g., WD and LMA).
Then you say that the low predictive power of these traits is because
they are poor surrogates of what we should be measuring --
i.e.~hydraulic traits. But then you end by saying that these are too
hard/expensive to measure, so you're going to look at other surrogates.

L102 \& L106: the introduction gives a nice overview of size and trait
influences on resistance to drought. But the third focus of your study
-- microenvironment characteristics -- gets little or no attention. In
fact it's not very clear what you mean by `microenvironment' for most of
the paper.

L150-152: Given that height is estimated and not measured, wouldn't it
be better to use DBH as a (measured) dimension of tree size?

L173: this is the first mention of what I'm guessing is your
`microenvironment' descriptor. Worth briefly mentioning why you are
measuring TWI.

@@

L230: Somewhere here it would be good to remind the reader what these
explanatory variables are.

L234-237: Not very clear how these models were constructed. Why did you
fit each predictor independently to test its importance as opposed to
standardizing them and having them together in a multiple regression and
then compare their coefficients? And why was height retained in all
models? Testing one predictor at a time might be sensible if you have
lots of collinearity between predictors. But it could also mean you miss
important conditional effects (e.g., the effect of variable x only
emerges when you first account for the effect of variable y).

L255-258: good to have this summary, but it's sort of expected that you
have a decline in growth as this is how you defined drought (a little
circular). So given that you've already mentioned how you defined
drought in the methods maybe you don't need to repeat this here?

L266-267: Don't think you can test the effects of crown dominance going
back this far. How can you be sure a tree was dominant/suppressed back
in 1966?

@@

L287: specify how they were related to drought. Positive? Negative?

Tables and Figures: there are a large number of tables. I wonder if
Table 2 and 3 would best fit in supporting information (with key
information integrated directly into the text). I also feel that it
would be nice to represent some of the key results (e.g., Rt and its
relationship to height and leaf hydraulic traits) in a figure.

\href{https://github.com/SCBI-ForestGEO/McGregor_climate-sensitivity-variation/issues/71}{\emph{issue
\#71}}

\hypertarget{referee-4}{%
\subsection{Referee: 4}\label{referee-4}}

@@

Comments to the Author

In this paper, McGregor et al.~study the effect of tree height, crown
position, ring-porosity, wood density, LMA and two leaf water relations
traits (percent loss of leaf area upon desiccation, PLA; and the turgor
loss point, TLP) on the drought resistance of 12 temperate species from
an oak-hickory forest of northern Virginia (USA). Drought resistance is
assessed using series of radial growth data and for the three most
severe droughts in the period 1950 - 2009 in the study area. The authors
find consistent negative effects of tree height on drought resistance;
effects of crown position, ring-porosity and water relation traits for
some droughts; and no effect of wood density and LMA. The paper is well
written and nicely organized around clear hypotheses. The results are
intriguing but, in my opinion, the experimental design is not strong
enough to clearly advance our understanding of the determinants of tree
drought responses.

Firstly, the way drought resistance (Rt) is estimated, as the ratio of
BAI during drought to the mean BAI over the five years preceding the
drought can be problematic, as growth dynamics during this pre-drought
period were quite variable across species (Figure 1; incidentally, why
do you show ring width indices in this figure if you then use BAI?).
This approach has also advantages, particularly when applied in a
resilience framework (as in the original Lloret et al.~(2011)). However,
if you focus specificaly on resistance it seems that directly modelling
the growth reduction caused by the drought (e.g., using intervention
time series analysis or other methods) would be a more robust approach.
At the very least, if you continue using your simpler approach I would
strongly suggest including some measure of pre-drought growth in the
models to account for differences in growth dynamics among species. It
would also nice to clarify why you do not assess recovery and
resilience, unlike Lloret et al.~(2011).

\href{https://github.com/SCBI-ForestGEO/McGregor_climate-sensitivity-variation/issues/92}{\emph{issue
\#92}}

\emph{add specifics (changes to text; SI table/fig \#s) to text below}

\textbf{In response to Reviewer 4's comments, we tried an intervention
time series analysis using the `auto.arima' function from the `forecast'
package ({\textbf{???}}). Specifically, we modeled BAI based on the
timeseries for the 10 years prior to the drought year (itself acting as
the intervention). We then recorded the ratio between the mean predicted
BAI and the observed BAI during the drought year, and compared these
results to \(Rt\). These yielded similar outcomes, which we now present
in the Supplementary Info. The original \(Rt\) and \(Rt_{ARIMA}\) were
fairly well correlated, but with some scatter (see figs below). To get a
sense of which metric was performing better, we visually reviewed the
records of the 18 trees with largest differences between \(Rt\) and
\(Rt_{ARIMA}\). \(Rt\) estimates were better for the majority of these,
and generally were not hugely unrealistic, whereas \(Rt_{ARIMA}\) could
be way off (e.g., for several trees that were undergoing growth declines
prior to drought and hit minima at or near the drought, \(Rt_{ARIMA}\)
was much greater than 1, suggesting a substantial growth increase during
the drought.). Thus, we decided to stick with \(Rt\) as the primary
metric.}

\begin{figure}
\centering
\includegraphics{tables_figures/publication/figureS4_Rt_arima_comparison.png}
\caption{Figure S4}
\end{figure}

\textbf{Regarding the resilience indices, we considered analyzing these
and decided it would be best to stick with just resistance for three
reasons: (1) Most importantly, we would expect resilience to be governed
by fundamentally different mechanisms than resistance. While it would be
interesting to examine resilience, this would be beyond the scope of the
current paper. (2)
\href{https://www.nature.com/articles/s41467-020-14300-5}{DeSoto et
al.~(2020, Nature)} used an extensive dataset of trees sampled after
severe droughts and compared the responses to previous, less-severe
droughts between trees that survived and trees that were killed by the
severe drought. In angiosperms, trees that died from a severe drought
had lower resistance to previous droughts, compared to trees that
survived the severe drought. In gymnosperms, trees that died during
severe droughts had lower recovery following previous droughts, compared
to trees that survived the severe drought. These findings would argue
that resistance is a more important variable for angiosperms. We now
state the logic for focusing on \(Rt\) in the methods section:}

\textbf{``We focus exclusively on drought resistance (\(Rt\) or
\(Rt_{ARIMA}\)), and not on the resilience metrics described in Lloret
\emph{et al.} (2011), because (1) we would expect resilience to be
controlled by a different set of mechanisms, and (2) the findings of
\emph{\href{https://www.nature.com/articles/s41467-020-14300-5}{DeSoto
et al.~(2020)}} suggest that \(Rt\) is a more important drought response
metric for angiosperms.''}

@@

Secondly, the choice of traits does not appear well justified, as it
seems to be driven more by easiness of measurement than by relevance,
and it mixes different types of hypotheses operating at different
levels. On one hand there is tree height and crown position, which are
measured at the level of individual trees and correspond to closely
related hypotheses. On the other hand there are ring-porosity, wood
density, LMA and water relations traits, which are measured at the
species level and seem to be totally disconnected from the hypotheses
regarding tree height. In addition, it is very hard to compare the
explanatory power of these variables, as done in the paper, as they are
based on very different sample sizes (571 trees vs 12 species) and
respond to different sources of variability. In fact the way height
effects are analyzed mixes the within- and between-species levels, which
makes it difficult to interpret the results. Finally, I think it would
be more correct to refer to PLA and TLP as water relations traits rather
than hydraulic traits.

Thirdly, a more thorough analysis of the distribution of the study
species in the sample plot would be required. The paper assumes that all
species were subjected to the same drought levels. However, this is
unlikely to be true, as different species are likely to occupy different
microhabitats in the plot, and hence be subjected to different drought
conditions. The authors account for this, to some extent, by including
individual-level TWI in some models, but a more thorough analysis of the
distribution of the study species as a function of TWI and other
relevant micro-environmental variables would be needed to fully
interpret the results.

\emph{It seems from these comments they think this shouldn't be
published at all due to its limited scope and not enough explanatory
power. The resulting study that they suggest, if completely thorough,
would take a long time to create. I'm not sure how to address this
comment, other than to make a note in the manuscript acknowledging that
a more thorough study would be great but this is what we found with what
we had.}

\emph{I agree\ldots. I wouldn't change analysis for this. We can come
back to wording a response later.}

@@

Minor or more technical suggestions:

L59-79: the arguments presented in this paragraph mix different scales,
from within-individual to within- or among-communities. I think the
arguments could be better structured to reflect the sources of
variability involved and, ideally, focus on the scale that will be
addressed in the paper.

L67: I suggest toning down the sentence to something like `Wider xylem
conduits are associated to higher vulnerability to embolism during
drought', as the mechanism linking wider conduits with embolism
vulnerability is far from clear and probably indirect.

@@

L81: you seem to use drought resistance and drought tolerance
interchangeably, which may be confusing. I think it is important to
clarify these definitions early on in the paper.

L97: `greater variation' that what?

L100-101: that is not true really. See for example Zhu et al.~(2018) in
Tree Phys, Farrell et al.~(2017) in PCE\ldots{}

@@

L137-140: mixing cores from dying and surviving individuals could be
problematic. Did you find any association between survival and previous
drought resistance? Was mortality different across species?

L160: you mean a log-log regression, right?

### 2020-07-16 manuscript/response_to_reviews.tex

L181: N=3 individuals per species is really quite low. In addition, by
sampling up to 8 m height you would probably be sampling less exposed
branches from taller trees, which could confound your results.

\emph{from NObby: ``Regarding the few individuals I would argue that
intraspecific SD was low (less than 10\% of the mean values). This
justifies - in my opinion - only sampling three individuals.''}

L188: `Wood'.

\textbf{Fixed.}

@@

L228-234: please clarify model structure. I understand you included tree
as a random factor only when the three droughts were analyzed together,
right? It would be nice to know what was the contribution of random
factors to model fit (only one R2 is shown in Table 5, and it is unclear
whether it corresponds to marginal or conditional values).

L238, 242, 244: it is unclear to me why in some cases you use a dAICc of
1 and sometimes of 2.

L287-299: it would be very useful to use scatterplots to show the
effects of traits on Rt in a figure.

\href{https://github.com/SCBI-ForestGEO/McGregor_climate-sensitivity-variation/issues/71}{\emph{issue
\#71}}

@@

L291-294: but this is problematic considering that you only had two
diffuse-porous species.

\textbf{We have made changes to the analysis that resulted in dropping
ring porosity from the full models. While we agree that it is
problematic that we only have two ring-porous species, we believe that
it's worth including because this engages with, and rejects, the
existing understanding that in this biome, ring-porous species are more
drought tolerant.}

@@

L297: TLP was significant for 1966 according to Table 4.

L301-302: I would tone down this, as your models explained a rather low
\% of the variation in Rt.

@@

L305-306: not for the 1977 and 1999 droughts, according to Table 5.

L314-316: or simply that your sample size was rather low. See also main
comments above.

L329-331: do you have any information on the demographic effects (e.g.,
mortality) of the three droughts studied?

\textbf{Unfortunately, no. All we could say is that the 1999 drought
didn't result in a big loss of live biomass.}

@@

Table 3: are DBH units correct? I suspect they should be mm instead of
cm.

\emph{These are incorrect. Ian, please convert to cm.}

Figure 1: please explain all acronyms.

\textbf{We now specify that these codes are given in Table 3.}

Figure 2: where are the leaf hydraulic traits shown (cf.~caption)?

\textbf{It was an error that this was mentioned in the caption; now
removed.}

Table S1: why only 11 species? Some of the fits are really low\ldots{}

\textbf{Bark thickness measurements were drawn from an existing data
set, and we did not make additional measurements because the trait is
unlikely to have meaningful influence on results. This study already
goes above and beyond the existing norm for accounting for bark
thickness in DBH reconstructions; typically there is no correction for
changes in bark thickness as the tree ages.}

Table S3: what does `rank' refer to?

\textbf{This has been clarified.}

@@

Figure S1: please add spatial scale to the figure.

\emph{IAN, please do this}

Figure S3: please specify that height values are estimated from
reconstructed DBH.

\textbf{Done.}

\hypertarget{citations}{%
\subsection*{Citations}\label{citations}}
\addcontentsline{toc}{subsection}{Citations}

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-bennett_larger_2015}{}%
\textbf{\textnormal{Bennett AC}, \textnormal{McDowell NG},
\textnormal{Allen CD}, \textnormal{Anderson-Teixeira KJ}}.
\textbf{2015}. Larger trees suffer most during drought in forests
worldwide. \emph{Nature Plants} \textbf{1}: 15139.

\leavevmode\hypertarget{ref-elliott_forest_2015}{}%
\textbf{\textnormal{Elliott KJ}, \textnormal{Miniat CF},
\textnormal{Pederson N}, \textnormal{Laseter SH}}. \textbf{2015}. Forest
tree growth response to hydroclimate variability in the southern
Appalachians. \emph{Global Change Biology} \textbf{21}: 4627--4641.

\leavevmode\hypertarget{ref-friedrichs_species-specific_2009}{}%
\textbf{\textnormal{Friedrichs DA}, \textnormal{Trouet V},
\textnormal{Büntgen U}, \textnormal{Frank DC}, \textnormal{Esper J},
\textnormal{Neuwirth B}, \textnormal{Löffler J}}. \textbf{2009}.
Species-specific climate sensitivity of tree growth in Central-West
Germany. \emph{Trees} \textbf{23}: 729.

\leavevmode\hypertarget{ref-helcoski_growing_2019}{}%
\textbf{\textnormal{Helcoski R}, \textnormal{Tepley AJ},
\textnormal{Pederson N}, \textnormal{McGarvey JC}, \textnormal{Meakem
V}, \textnormal{Herrmann V}, \textnormal{Thompson JR},
\textnormal{Anderson‐Teixeira KJ}}. \textbf{2019}. Growing season
moisture drives interannual variation in woody productivity of a
temperate deciduous forest. \emph{New Phytologist} \textbf{0}.

\leavevmode\hypertarget{ref-kannenberg_linking_2019}{}%
\textbf{\textnormal{Kannenberg SA}, \textnormal{Novick KA},
\textnormal{Alexander MR}, \textnormal{Maxwell JT}, \textnormal{Moore
DJP}, \textnormal{Phillips RP}, \textnormal{Anderegg WRL}}.
\textbf{2019}. Linking drought legacy effects across scales: From leaves
to tree rings to ecosystems. \emph{Global Change Biology} \textbf{0}.

\leavevmode\hypertarget{ref-liu_hydraulic_2019}{}%
\textbf{\textnormal{Liu H}, \textnormal{Gleason SM}, \textnormal{Hao G},
\textnormal{Hua L}, \textnormal{He P}, \textnormal{Goldstein G},
\textnormal{Ye Q}}. \textbf{2019}. Hydraulic traits are coordinated with
maximum plant height at the global scale. \emph{Science Advances}
\textbf{5}: eaav1332.

\leavevmode\hypertarget{ref-lloret_components_2011}{}%
\textbf{\textnormal{Lloret F}, \textnormal{Keeling EG}, \textnormal{Sala
A}}. \textbf{2011}. Components of tree resilience: Effects of successive
low-growth episodes in old ponderosa pine forests. \emph{Oikos}
\textbf{120}: 1909--1920.

\leavevmode\hypertarget{ref-olson_plant_2018}{}%
\textbf{\textnormal{Olson ME}, \textnormal{Soriano D},
\textnormal{Rosell JA}, \textnormal{Anfodillo T}, \textnormal{Donoghue
MJ}, \textnormal{Edwards EJ}, \textnormal{León-Gómez C},
\textnormal{Dawson T}, \textnormal{Martínez JJC}, \textnormal{Castorena
M} \emph{et al.}} \textbf{2018}. Plant height and hydraulic
vulnerability to drought and cold. \emph{Proceedings of the National
Academy of Sciences} \textbf{115}: 7551--7556.

\leavevmode\hypertarget{ref-stovall_tree_2019}{}%
\textbf{\textnormal{Stovall AEL}, \textnormal{Shugart H},
\textnormal{Yang X}}. \textbf{2019}. Tree height explains mortality risk
during an intense drought. \emph{Nature Communications} \textbf{10}:
1--6.

\leavevmode\hypertarget{ref-zuleta_drought-induced_2017}{}%
\textbf{\textnormal{Zuleta D}, \textnormal{Duque A},
\textnormal{Cardenas D}, \textnormal{Muller‐Landau HC},
\textnormal{Davies SJ}}. \textbf{2017}. Drought-induced mortality
patterns and rapid biomass recovery in a terra firme forest in the
Colombian Amazon. \emph{Ecology} \textbf{98}: 2538--2546.

\end{document}
